\documentclass{article}
\begin{document}

\title{Software Requirements Specification for Mashbot} 
\author{George D'Andrea \and \and Andrew Gall \and Josiah Kiehl \and
  Cody Ray \and Vito Salerno}
\date{\today}
\begin{titlepage}
\maketitle
\end{titlepage}

\tableofcontents

\section{Introduction}

\subsection{Purpose} % JK
This document is the general overview of the requirements for the Mashbot project.  The sections below are specifically ``what'' is to be done as opposed to ``how'' it is to be done.
\subsection{Scope} % JK
This document covers a high level overview of what features a successful project delivery will include.
\subsection{Glossary} % Everyone
\subsection{Overview} % CR

\section{Overall Description}
     \subsection{Product Perspective}
		For many startups and small businesses, marketing /
                customer service and business / development efforts
                compete for scarce resources.  Furthermore, early
                stage startups often have small or non-existent
                marketing budgets, especially in resource-hungry
                product-based startups.  Although the plethora of
                widely available and affordable communications
                technology (e.g., social media, VoIP, streaming video,
                etc.) theoretically reduces both capital and operating
                expenditures related to marketing, the quantity of
                such technologies and services effectively creates an
                "opportunity overload" making the process of
                maintaining a focused and effective marketing campaign
                more difficult.  Furthermore, with the number of
                services, technologies, and "specialists" arriving
                each day, its nearly impossible to keep up with all
                the trends much less to fully take advantage of each
                or even monitor them all adequately! As you can see,
                the widespread adoption of communications technology
                is a double-edged sword---there are many more avenues
                for marketing and customer service, but it is much
                more difficult to effectively apply reputation
                management strategies or adequate customer service
                through all channels. This project proposes to build a
                tool to increase the effectiveness and efficiency of
                marketing campaigns and customer service for small to
                medium businesses.
		\subsubsection{System Interfaces} % VS
			Mashbot combines several components to provide the functionality
			required.
			\begin{itemize}
				\item \textbf{Authentication} Mashbot
                                  will allow the use of external
                                  authentication modules for user
                                  login. Mashbot will also provide an
                                  internal authentication mechanism
                                  in case an external module is
                                  unavailable.
				\item \textbf{Campaign Manager Web
                                  Client} Mashbot has an interface for
                                  a web client which processes user's
                                  commands to interact with campaigns.
				\item \textbf{Publishing and Aggregation
                                  Platform}
				\item \textbf{Database} Mashbot has an
                                  interface to a database which allows
                                  for the storage and retrieval of
                                  data related to accounts and campaigns.
			\end{itemize}
		\subsubsection{User Interface} % JK
                The user interface consists of a web front end
                with tabs to separate the various workflow areas. To
                create content, the user is provided with a calendar
                scheduling tool, and a content editor.  Additionally,
                there is a monitoring dashboard which gives the user a
                view on responses to the content in any given campaign.
                Finally, there is an explore view that gives the user a
                portal with which they can keep tabs on topics of 
                interest in social media.
		\subsubsection{Hardware Interfaces} % VS
                The Mashbot web client runs on any computer hardware meeting
                the following criteria:
                \begin{itemize}
                  \item Capable of connecting to the Internet
                  \item Capable of running a modern HTTP 1.1 web browser
                  \item Includes a keyboard and a pointing device
                  \item Includes writable volatile storage
                \end{itemize}
                The Mashbot server runs on any computer hardware meeting
                the following criteria:
                \begin{itemize}
                \item Capable of connecting to the Internet as a server.
                \item Capable of interfacing with modern database software.
                \item Capable of running a modern suite of networking software.

		\subsubsection{Software Interfaces} % VS
                The Mashbot software integrates some external software
                to provide functionality.
                \begin{itemize}
                \item \textbf{Authentication} Mashbot authenticates users
                  against it's internal user database.
                \item \textbf{Campaign Manager Web Client} Mashbot
                  interfaces with the user’s web browser and expects
                  that it is capable of HTTP 1.1 and HTML 4.0.
                \item \textbf{Database} Mashbot software interfaces
                  with an existing database software.
                \item \textbf{Server} The Mashbot server software runs
                  on an operating system that supports serving dynamic
                  web pages using encryption and is capable of
                  communicating with the Internet.
                \end{itemize}
		\subsubsection{Communications Interfaces} % VS
                   Communication between the web client and the
                   server software is facilitated by common network
                   protocols. This allows compatibility with the
                   majority of our user's machines.  Data will
                   be encrypted using TLS and HTTP/1.1. The use of
                   these protocols requires the ability for the
                   systems to communicate using TCP/IP network stacks.
                   The Mashbot system sends emails using SMTP.

		\subsubsection{Memory Constraints} % VS
                The Mashbot server requires no greater than 1 gigabyte
                of RAM memory. The web client requires no more than
                the minimum memory a modern desktop computer commonly
                has, approximately 256 megabytes of RAM.

	\subsection{Product Functions} % AG
        Mashbot should be able to:
        \begin{enumerate}
          \item Schedule content for various services to be
            published concurrently
          \item View and Compare historical metrics of campaigns
          \item View/Create replies to content
          \item Maintain users and approvers of content
          \item Set up keyword alerts for ``watched'' services
        \end{enumerate}
	\subsection{User Characteristics} % AG
        The target user is a small to medium business employee who understands
        the basic capabilities of social media.
        
	\subsection{Requirements Apportioning} % VS
        \begin{tabular}{|c|p{4in}|}
          \hline
          \textbf{Priority} & \textbf{Description} \\
          \hline \hline
          1 & Mashbot can not be released unless it satisfies these
              requirements. \\
          \hline
          2 & Mashbot may be initially released without satisfying these
              requirements. Having these requirements unfulfilled must
              not create dangers to the system. They should be implemented in the next
              minor release. \\
          \hline
          3 & These requirements are not expected to be fulfilled by
              the initial release of Mashbot, but should be
              implemented in the next major release. \\
          \hline
          4 & These requirements are outside the current scope of the
              project, but are included to exhibit how our software
              will improve in the future. \\
          \hline
        \end{tabular}

\section{Specific Requirements}
	\subsection{External Interface Requirements}
	\subsection{Functional Requirements}
		\subsubsection{User Accounts} % AG
			\begin{itemize}
				\item \textbf{User Account Types and Permissions} The system categorizes users on the basis
				of roles and privileges. Within these roles, the system also categorizes users based on
			 	the roles that they have within individual products.	These are referred to as user 
				account roles.
				\begin{itemize}
					\item Mashbot! Campaigns supports the following account roles:
						\begin{enumerate}
							\item Content Approver
							\item Content Creator
							\item Content Editor
							\item Content Release Scheduler
							\item Content Responder
							\item Product Administrator
							\item System Administrator
						\end{enumerate}
					\item A user may possess more than one role.
					\item Roles reflect actions that can be performed by a user.
					\item Roles can be assigned to a user account for individual products.
					\item \textbf{Content Approver} can approve for release content which has been
					submitted for approval
					\item \textbf{Content Creators} may create new content or import existing
					content into the system. They may also submit this content for approval.
					\item \textbf{Content Editor} may edit content which has already been posted to external
					services.
					\item \textbf{Content Release Scheduler} may schedule or immediately initiate the release 
					to external services of content which has already been submitted and approved.
					\item \textbf{Content Responder} may respond to responses which have been made to the posted 
					content within the external services.
				 	\item \textbf{Product Administrator} is responsible for setting individual roles for a product.
						\begin{itemize}
							\item There must be at least one product administrator for each product.
						\end{itemize}	
					\item \textbf{System Administrator} can perform any of the roles in the system for any product.
					Additionally, they can set any system-wide settings which effect all products in the system.
				\end{itemize}
			\end{itemize}

		\subsubsection{Products} % AG
			\begin{itemize}
				\item \textbf{Product Types} The system categorizes products based on the type of content they push.
			 		These are referred to as product content types.
				\begin{itemize}
					\item Mashbot! Campaigns support the following product content types:
						\begin{enumerate}
							\item Blog
							\item Pictures
							\item Status
							\item Video
						\end{enumerate}
					\item A product may possess more than one content type.
					\item \textbf{Blog} may be added, removed, edited, and replies may be collected and responded to. 
					\item \textbf{Pictures} may be added, removed, and replies may be collected and responded to.
					\item \textbf{Status} may be added, removed, edited, and replies may be collected and responded to. 
					\item \textbf{Video} may be added, removed, and replies may be collected and responded to.
				\end{itemize}	
			\end{itemize}
		\subsubsection{Marketing Campaigns} % JK
                A campaign is a collection of content that is scheduled to be published by the company using mashbot.
                \begin{itemize}
                  \item Name
                  \item Pieces of content
                  \item Schedule
                  \item User/Group Permissions
                \end{itemize}
                A campaign's schedule is a set of dates and times that a piece of content has some action taken upon in.  Any action can be scheduled: post, edit, delete.
                
                Example: A series of tweets, blog posts and you tube videos need to be published for the release of a Product X.  These are all added to a Campaign.  The user may then use the Campaign's calendar to schedule these pieces of content for publishing
		\subsubsection{External Service Accounts} % JK
                An external service account is a set of credentials and/or an authentication token which allows Mashbot to connect to services.  The requirements for ESAs vary from service to service, where one service might provide token based authentication where another will provide only username/password.
	\subsection{Security Requirements} % VS 
	\subsection{Design Constraints} % CR
	\subsection{Software System Attributes} % AG
	\subsection{User Interface} % JK
        The user interface is to be clean and crisp. There is to be a tabbed navigation bar that unifies the sitewide navigation, as well as module specific navigation as needed.  

\section{Preliminary Analysis} % JK

\section{Use Cases} % CR

%% \section{IO}

%% Inputs
%%   CRUD
%%   Types
%%     Pictures
%%     Status/Tweet
%%     Blog
%%     Video

%% Users
%%   Name
%%   Email
%%   Company
%%   Permissions
%%   Accounts
    
%% Account
%%   What a company buys
%%   Allows user/campaign creation
  
%% Campaigns
%%   Name
%%   Schedule
%%   Content
%%     Distribution Channels


\end{document}


% LocalWords:  Mashbot
